---
title: Quantifying effect sizes in implicit learning tasks; the role of some stuff
authors:
  - name: Kelly G. Garner
    thanks: Corresponding author
    department: School of Psychology
    affiliation: University of Birmingham
    location: Edgbaston, UK, B13 2TT
    email: getkellygarner@gmail.com
  - name: Christopher R. Nolan
    department: School of Psychology
    affiliation: University of New South Wales
    location: Sydney, Australia
    email: cnolan@cn.id.au
  - name: Ole Jensen
    department: School of Psychology
    affiliation: University of Birmingham
    location: Edgbaston, UK, B13 2TT
    email: o.jensen@bham.ac.uk
  - name: Markus Barth
    department: Centre for Advanced Imaging
    affiliation: University of Queensland
    location: St. Lucia, Australia, 4072
    email: m.barth@uq.edu.au   
  - name: Saskia Bollmann
    department: Centre for Advanced Imaging
    affiliation: University of Queensland
    location: St. Lucia, Australia, 4072
    email: saskia.bollmann@cai.uq.edu.au
  - name: Marta Garrido
    department: School of Psychological Sciences
    affiliation: University of Melbourne
    location: Parkville, Australia, 3010
    email: marta.garrido@unimelb.edu.au
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: refs.bib
biblio-style: unsrt
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
  bookdown::word_document2:
    toc: true
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
#opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE)
options(digits = 3, width = 88, knitr.graphics.auto_pdf = TRUE,
        knitr.kable.NA = '')
```

```{r, libraries, echo=FALSE, message=F, warning=F}
library(magrittr)
library(tidyverse)
library(cowplot)
library(readr)
library(wesanderson)
library(RJSONIO)
library(cowplot)
library(rlang)
library(kableExtra)
library(scales)
library(rstatix)
library(lme4) 
library(emmeans)
source("../R/R_rainclouds.R") # for the raincloud plot
source("../R/data_wrangles.R")
#source("R/R_rainclouds.R") 
```


\clearpage

# Introduction

\label{sec:Introduction}

Characterizing the neurophysiology that underpins the brain's ability to filter and extract goal-relevant information from the visual world has been a priority in neuroscience for multiple decades [e.g. @desimoneNeuralMechanismsSelective1995, @buschmanBehaviorNeuralDynamics2015a]. At the cortical level, visual information processing has been relatively well mapped out; many observations have demonstrated the correspondence of neural activity in frontal, parietal and visual cortices to the biasing of the visual system towards the specific the specific spaces or features that have been indicated as goal-relevant, i.e. visual selection [@buschmanBehaviorNeuralDynamics2015a, @corbettaControlGoaldirectedStimulusdriven2002]. However, the putative contribution of less interrogated subcortical structures such as the basal ganglia has only more recently become evident. For example, electrophysiological recordings from macaques indicate that cells in the caudate nucleus (CN) respond to the joint location and identity of objects [@yamamotoWhatWhereInformation2012], and contribute to the circuitry that guides both eye-movements [@amitaOptogeneticManipulationValuecoding2020] and covert attention shifts [@arcizetCovertSpatialSelection2018] towards goal-relevant objects. Furthering theory for how the brain performs visual selection therefore requires an understanding of how subcortical and cortical structures interact to produce behaviour. Attaining this understanding in the human model is not a simple task, given the relative inaccessibility of basal ganglia activity to non-invasive imaging approaches. 

One potentially fruitful avenue is the utilisation of high-resolution functional magnetic resonance imaging (fMRI). Imaging the functional activity of the basal ganglia is challenging for multiple reasons. First, the relatively higher iron content of the nuclei of the basal ganglia [@drayerMagneticResonanceImaging1986] results in shorter $T^{*}_{2}$ relaxation times (~15 ms) compared to the cortex (~25-35 ms, @keukenUltraHigh7TMRI2013, @petersT2MeasurementsHuman2007, vanderzwaagFMRICharacterisingBOLD2009, yacoubImagingBrainFunction2001]). For optimal BOLD-sensitivity, the echo time (TE) of a single echo-planar imaging (EPI) protocol should be equal to the $T^{*}_{2}$ of the tissue of interest [Posse, 1999]. Therefore, striking a balance in TE values to capture signal at both subcortex and cortex is not without challenge. [Have a chat with Markus about this section]. 
Introduce multi-echo, CMRR and 3D EPI].

This challenge has been well addressed in previous works that have sought to image functional basal ganglia activity during performance of overt actions at 7T. For example, Puckett et al [-@puckettUsingMultiechoSimultaneous2018] compared outcomes for SE and ME SMS EPI protocols when participants performed an overt action task that involved simple and complex sequences of self-paced button presses. The theoretical contribution of the basal ganglia to overt action is well documented [see Caligiore et al, 2017, Gurney et al, 2004 for reviews], and therefore imposing a cognitive challenge during overt action selection is the ideal starting point for determining the potential of 7T ME imaging for improving signal quality in the basal ganglia. The authors found that signal quality was improved for the ME relative to the SE protocol, notably in CN and the putamen (Put). Furthermore, the extent of the improvement was negatively related to the underlying $T^{*}_{2}$ of the voxels. Therefore, signal from the tissues with shorter $T^{*}_{2}$, such as the basal ganglia, showed the greatest signal improvements with the ME protocol. In contrast, Militec et al [-@mileticFMRIProtocolOptimization2020] compared ME and SE protocols during performance of a stop-signal task where participants execute or withhold an overt motor response depending on a given visual signal. The authors sought to optimise protocol parameters in order to attain whole brain coverage, while maintaining the spatial and temporal resolution required to capture signal from subcortical regions. Specifically, they held spatial resolution constant at 1.6 mm isotropic, and increased parallel acceleration to attain a ME sequence. The authors found only marginal differences between protocols, suggesting that the advantages of a ME sequence may be limited when testing more subtle manipulations of overt action control. It remains unknown whether this holds under conditions where there are theoretical reasons to believe the basal ganglia makes a functional contribution in the absence of overt actions, such as during a covert visual selection task.

We therefore sought to compare between EPI protocols from images collected while participants performed a cued visual-selection task. Participants monitored two locations for an upcoming oriented gabor, which was preceded by cues that indicated the likely location or the incentive value of the upcoming gabor. The current work focuses on the spatial cue aspect of the paradigm for the following reasons; the influence of spatial cues on visual-selection has been documented over multiple decades (e.g. @posnerOrientingAttention1980, @carrascoVisualAttention252011, @chicaSpatialOrientingParadigm2014), particularly in relation to corresponding cortical activity [@corbettaControlGoaldirectedStimulusdriven2002, @desimoneNeuralMechanismsSelective1995, @fiebelkornDynamicInterplayFrontoparietal2018], and has been the subject of recent scrutiny with regard to the contribution of basal ganglia/cortical interactions [@wangInvolvementStriatalDirect2020, @arcizetCovertSpatialSelection2018, @hermanAttentionrelatedModulationCaudate2020]. The incentive value cues were included in the current paradigm as this task formed the basis for a larger, ongoing study that seeks to map the human brain networks whose functional activity corresponds to both cue types, which will be reported elsewhere. 

Thus we compared the signal yielded between ME and SE multi-band and 3D EPI protocols at 7T, deployed as participants completed a task where spatial cues modulated expectancies with regard to upcoming targets. To assess signal quality we compared both temporal signal-to-noise (tSNR) and contrast-noise (CNR) ratios. tSNR, computed as the ratio of the mean of the timeseries relative to the standard deviation of the timeseries ($\frac{mu_{T}}{\sigma_{T}}$) provides a measure of the strength of the activation signal of the time course, relative to several sources of noise such as system, physiological and task-related. The measure of the activation signal contains both baseline signal and task-related fluctuations. Thus the measure of tSNR quantifies how the global signal level is related to the noise of the signal [@welvaertDefinitionSignalToNoiseRatio2013]. CNR measurements were defined by taking the $t$-score from contrasts of interest that are defined below. 

-> motivate tSNR and CNR e.g. For a measure of BOLD-sensitivity to each contrast, the resulting _t_-scores were used as a measure of activation sensitivity. Temporal SNR measures, once augmented to account for temporal correlations in the data, amount to computing the _t_-score for the mean signal change; i.e. the _t_-score serves as a contrast-to-noise ratio (CNR) measure  [@corbinAccurateModelingTemporal2018]. 
-> performed signal comparisons on the basis of where strongest signal vs meta-analytic/regional approach \@ref{fig:aims}

We chose to model response hand as motoric contrasts are typically used to assess sensitivity of imaging sequences to signal in the basal ganglia [@puckettUsingMultiechoSimultaneous2018; mileticFMRIProtocolOptimization2020], and this therefore provides a good basis for comparison to the results attained when modelling the attentional manipulations of interest. 

the main effect of response hand (left hand vs right hand response), as this manipulation is most likely to yield the largest differences in the basal ganglia e.g. [@puckettUsingMultiechoSimultaneous2018]. the main effect of target laterality (left vs right), as previous evidence suggests that cells in the striatum respond to combined object location and identity [@yamamotoWhatWhereInformation2012]. The main effect of cue probability (p=.5 vs .8), as the basal ganglia has been hypothesised to encode the probability of sensory inputs in visual decision making [@caballeroProbabilisticDistributedRecursive2018]. The cue probability x target location interaction, to ascertain sensitivity to the lateralised expectation and inhibition that has been hypothesised to occur when spatial targets enable prioritisation of locations for upcoming target processing [@schmitzNormalizationCholinergicMicrocircuit2018; @reynoldsNormalizationModelAttention2009].


```{r aims, out.width = "50%", fig.cap="Regions of interest. A) Basal Ganglia anterior view, B) Basal Ganglia posterior view, C) Cortical ROIs. CN = Caudate Nucleus, GPe = Globus Pallidus External, GPi = Globus Pallidus Internal, Put = Putamen, STN = Subthalamic Nucleus, VS = Ventral Striatum, FEF = Frontal Eye Fields, IPS = Intraparietal Sulcus, LOC = Lateral Occipital Complex"}
paradigm.fig.pth <- '../images/Fig_ROIs.png'
#paradigm.fig <- readPNG(paradigm.fig.pth, native=TRUE, info=TRUE)
include_graphics(paradigm.fig.pth)
```


# Methods
\label{sec:Methods}


## Participants
\label{sec:Participants}

A total of 5 participants [1 female, 1 left-handed, mean age: 30.6 yrs, std: 7.7] took part in the experiment. Participants had normal or corrected-to-normal vision, and all reported no major neurological or psychiatric diagnoses, or use of psychoactive medications. All participants received 20 AUD per hour for participation. Participants also earned cash rewards, contingent on the accuracy and speed of responses in the presence of incentive value cues (~15 AUD per session). The University of Queensland Human Research Ethics Committee approved the study as being within the guidelines of the National Statement on Ethical Conduct in Human Research and all participants gave informed, written consent.

## Experimental Protocols
\label{sec:Protocols}

Participants attended four experimental sessions; an initial behavioural session, where participants learned the the task procedures, and three sessions in the MRI scanner. A full description of the initial behavioural session can be found online [here](). 
  
### Behavioural Paradigm
\label{sec:BehavParadigm}

We adapted a previously published spatial cueing task where participants made orientation judgements to a visual target, while ignoring a distractor. The target and distractor are prececed by probabilistic spatial and incentive value cues [@garnerIncentiveValueSpatial2021] (see Figure \@ref{fig:paradigm}). Note that while we used a combination of value and spatial cues, as we intend to use both in future work, we currently focus on only the influence of spatial cues, given the robustness and size of this effect [@posnerOrientingAttention1980; @chicaSpatialOrientingParadigm2014] and our current sample size.               

### Experimental Task Apparatus
\label{sec:Apparatus}

Experimental procedures were run using a [blah blah PC]. Visual displays were projected with a [blah blah] projector, to a [blah blah] screen with a FOV of 358 x 230 mm, a resolution of 1600 x 1200 pixels, and a refresh rate of 60 Hz. Distance from the coil mirror to the projector screen was 1300 mm, and the distance of the participant to the coil mirror was approximately 50 mm. The experimental procedures were implemented using custom written software for Matlab 2018b and Psychtoolbox v3.0.15 [@brainardPsychophysicsToolbox1997; @pelliVideoToolboxSoftwareVisual1997]. 


### Stimuli
\label{sec:Stimuli}

All stimuli were presented on a grey [RGB: 128, 128, 128] background. A grey cross [RGB: 115, 115, 115] superimposed over a diamond (rotated white square [RGB: 191, 191, 191, 45$^\circ$]) was presented in the centre of the screen and served as a fixation point. The grey cross subtended 0.8$^\circ$ visual angle, and the diamond subtended 1.6$^\circ$. A leftward or rightward facing triangle [RGB: 90, 90, 90], superimposed on one half of the white diamond served as the informative spatial cue (p=.8). Simultaneous presentation of both triangles served as an uninformative spatial cue (p=.5). The two triangles together comprised 80 % of the surface area of the underlying white square. Two coloured discs (!x! $^\circ$ in diameter, matched for luminance; [gold RGB: 182, 133, 58, rose RGB: 230, 93, 85]) served as value cues. These were presented 5.5$^\circ$ from the centre along, and 2$^\circ$ below  the horizontal meridian. Further information on the value configurations are presented in the procedure section below. Target and distractor stimuli were presented within the value cue discs. Targets were a gabor (3$^\circ$ in diameter, standard deviation of the Gaussian envelope, 0.3; spatial frequency, 2.5/ppd (pixels per degree)) oriented 45$^\circ$ clockwise or counter-clockwise. Distractors shared the same visual features except they were presented on one of the cardinal axes. The distance of the target and distractor from the centre was chosen so that the viewer could discriminate the gabors without making an eye-movement, while remaining just within the locus of high-acuity vision (~6$^\circ$). The target and distractors were followed by mask stimuli, which consituted a patch of pixels randomly weighted between the background grey and white, weighted by the same Gaussian envelope as was used for the target and distractor. Feedback reward values were presented centrally in alphanumeric characters, and were presented in yellow in the case of correct responses (i.e. in the case of reward gain, [RGB: 255, 215, 0]), and in grey [RGB: 90, 90, 90] for errors. 

### Behavioural Procedure
\label{sec:BehavProcs}

As shown in Figure \@ref{fig:paradigm}, each trial began with the the central fixation display (cross and diamond). The duration of this display varied across the protocols as we adjusted visual display onsets to coincide with the TR pulses sent from the MRI scanner ($a_t$; ME: 1100 ms, CMRR: 2020 ms, 3D-EPI: 2840 ms). The duration of the key visual events was held constant across all three protocols. Nexr, the fixation cross was removed and the value cues onset. After 400 ms, the spatial cue was presented for 300 ms. The target and distractor were presented after a random interval between 0-100 ms after spatial cue offset (selected from a uniform distribution). The target and distractor were displayed for 67 ms, and were followed by the masks which were displayed for 67 ms. The orientation of the target (45$^\circ$ clockwise or counterclockwise) and the distractor (vertical or horizontal) was fully counterbalanced across target-distractor pairing, location, and cueing condition. The value cues and central white diamond remained on display during the response interval [$b_t$; ME: 1826-1926 ms, CMRR: 2136-2146 ms, 3D EPI: 946 - 1046 ms]. Next, reward feedback was presented contingent on the participant's response. The duration of the feedback display was 1000 ms for both correct and incorrect responses. For correct responses, the maximum reward value available was weighted ($w$) by the proportion of the participant's response time (RT) of a given range (350 ($RT_{min}$) - 850 ($RT_{max}$) ms) - i.e. $w= \frac{RT_t - RT_{min}}{RT_{max} - RT_{min}}$. For the reward feedback display, the previous reward total was displayed on the left followed by a plus sign and the reward value attained on that trial to the right. Over the next second, the new reward value counted down as the previous reward value increased, over 50 ms intervals. In the case of an incorrect response, the previous points total was displayed in dark grey in the centre of the screen. 

**Value cue configurations** 
Each value cue colour signalled the probability of attaining a high value reward, relative to attaining a low value reward, should the target appear at that location (see Figure \@ref{fig:paradigm}, Panel B). For example, for a given participant, the gold colour would predict a high reward value with p = .8, and therefore signalled a higher expected reward value ($H$). In contrast, the rose colour would predict a high reward value with p = .2, and would therefore signal a lower expected reward value ($L$). Value cues were presented in 4 different possible combinations, which where fully counterbalanced over location (left vs right), and from now are coded in relation to the location where the upcoming target and distractor appeared; 1) both the target and distractor locations could contain the high expected reward value colour ($H_{tgt}/H_{dst}$), 2) both locations could contain the low expected reward value colour ($L_{tgt}/L_{dst}$), 3) the target location could contain the high expected reward value colour, whereas the distractor location contained the low expected value colour ($H_{tgt}/L_{dst}$), or 4) vice-versa ($L_{tgt}/H_{dst}$). Participants learned the colour-reward associations in the previous behavioural session, specific colour-reward mappings were counterbalanced over participants. 

**Spatial cue probabilities** 
Directional spatial cues (see Figure \@ref{fig:paradigm}, panel C) carried a p = ~.8 (.78) chance of validly signalling the upcoming target location. Bidirectional cues signalled either location with p = .5. Across each functional run, there were 72 trials containing a directional cue (56 valid, 16 invalid), and 56 trials containing a bidirectional cue. Laterality of target location was fully counterbalanced over all cue conditions. Note that when modelling the fMRI data focus on comparisons between the valid (p=.8) and bidirectional (p=.5) conditions. We don't make comparisons between these and the invalid trials, given the latter's lower trial numbers and consequent higher likelihood of variance differences to the other conditions. The reward available was matched across the spatial cueing trials, so that neither spatial cue condition (p=.2, .5, .8) nor location (left vs right) predicted a greater reward value than another. 

Participants had received extensive instructions and training in the aforementioned task during the initial behavioural session, the details of which can be found [here](). In addition to these instructions, participants were requested to remain as still as possible during the functional runs.

<br>  

```{r paradigm, out.width = "70%", fig.cap="Cueing paradigm. A) Trial sequence, B) value- and C) spatial-cue contingencies, D) Behaviour: Inverse efficiency (RT/accuracy) given the probability of the target location, shown for each each protocol. Error bars reflect SEM. T=target, D=distractor, CW=clockwise, CCW=counterclockwise, ME=multi-echo, CMRR=, 3D=3D Echo Planar Imaging"}
paradigm.fig.pth <- '../images/ParadigmBehav.png' 
include_graphics(paradigm.fig.pth)
```


## Scanning Procedures
\label{sec:ScanProcs}

Each participant was scanned over three sessions, on a 7T MRI system (Siemens Healthineers, Germany) using a 32-channel phased array headcoil (Nova Medical, Wilmington, US). Within each session, participants completed 3 functional runs, 1 for each protocol (see Table \@ref(tab:acquistable) for protocol details). For each participant, all three sessions took place at the same time of day. Each session started with a short localizer scan, the anatomical scan, and then the 3 functional runs. The order of the protocols used for each functiona run was randomised across sessions. The functional runs varied slightly in duration, owing to the differences in the inter-trial-interval, which was dependent on the TR of each protocol (ME = 10:52 mins, CMRR = 13:02, 3D EPI = 12:44).

Participant #1 completed only the first two sessions, due to scheduling error. For participant #3, the 3D EPI was stopped early in the third scanning session, rendering it impossible to reconstruct the images. All remaining data was included in the analysis.

### MR Protocols
\label{sec:MRProts}

The details for each of the functional protocols are defined in Table 1. Each was chosen to yield high resolution while maintaining the field of view (FOV) required to assess BOLD activity changes in both the subcortical and cortical ROIs.

The MP2RAGE was acquired with the following parameters: TR = 4300 ms, TE = 3.38 ms, 0.8 mm isotropic, T1 1 = 840 ms, T1 2 = 2370 ms, flip angle 1 = 5$^\circ$, flip angle 2 = 6$^\circ$, FOV = 240 mm x 225 mm x 192 mm. 

```{r acquistable, echo=FALSE, message=F, warning=F}

# Show it:
TRs <- data.frame(TR=c(700, 1510, 1920), 
                  TE=c('10, 30.56','19.4','22'),
                  VoxSizeIso = c(2, 1.5, 1.5),
                  PhaseEncodingDirGRAPPA = c('2','3','2'),
                  MultiBandFactor=c('4','3','CAiPI shift 1'),
                  ExcitFlipAngle=c(35,60,15),
                  ReceiverBand_Hz_Px=c(1930,1116,1116),
                  partFourier=c('5/8','6/8','6/8'),
                  FOV=c('192 x 192 x 96','192 x 192 x 122','192 x 192 x 120'),
                  Nslices=c(48,81,80))
rownames(TRs) <- c("ME", "CMRR", "3DEPI")
kable(t(TRs), caption="Table 1. Compared Protocols") %>% kable_classic(full_width=F, html_font="Cambria")

```

### Preprocessing
\label{sec:Preproc}

All anatomical and functional data were preprocessed using _fMRIprep_ (version 1.5.8; [estebanFMRIPrepRobustPreprocessing2019]), which is based on _Nipype 1.4.1_ [@gorgolewskiNipypeFlexibleLightweight2011, @estebanNipyNipype2020]. 

**Anatomical data preprocessing** 
Each T1-weighted (T1w) image was corrected for intensity non-uniformity (INU) with `N4BiasFieldCorrection` [@tustisonN4ITKImprovedN32010], distributed with ANTs 2.2.0 [@avantsSymmetricDiffeomorphicImage2008, RRID:SCR_004757]. The T1w-reference was then skull-stripped with a *Nipype* implementation of the `antsBrainExtraction.sh` workflow (from ANTs), using OASIS30ANTs as target template. Brain tissue segmentation of cerebrospinal fluid (CSF), white-matter (WM) and gray-matter (GM) was performed on the brain-extracted T1w using `fast` [FSL 5.0.9, RRID:SCR_002823, @zhangSegmentationBrainMR2001]. A T1w-reference map was computed after registration of 3 T1w images (after INU-correction) using `mri_robust_template` [FreeSurfer 6.0.1, @reuterHighlyAccurateInverse2010]. Brain surfaces were reconstructed using `recon-all` [FreeSurfer 6.0.1, RRID:SCR_001847, @daleCorticalSurfaceBasedAnalysis1999], and the brain mask estimated previously was refined with a custom variation of the method to reconcile ANTs-derived and FreeSurfer-derived segmentations of the cortical gray-matter of Mindboggle [RRID:SCR_002438, @kleinMindbogglingMorphometryHuman2017]. Volume-based spatial normalization to one standard space (MNI152NLin2009cAsym) was performed through nonlinear registration with `antsRegistration` (ANTs 2.2.0), using brain-extracted versions of both T1w reference and the T1w template. The following template was selected for spatial normalization: *ICBM 152 Nonlinear Asymmetrical template version 2009c* [@fonovUnbiasedNonlinearAverage2009, RRID:SCR_008796; TemplateFlow ID: MNI152NLin2009cAsym]. 

**Regions of Interest**
Of pertinent interest to the current work was the sensitivity of the three protocols to activation in the basal ganglia and in cortical nodes that have been consistently related to visual selection behaviours. Thus, ROIs were selected based on human basal ganglia anatomy, and for cortical regions of interest; on a meta-analysis of previous findings.

_Nuclei of the Basal Ganglia_: The ROIs from the basal ganglia were the caudate nucleus (CN), the ventral striatum (VS), putamen (Put), globus pallidus external (GPe), globus pallidus internal (GPi), and the sub-thalamic nucleus (STN). These were identifed using a published atlas derived from high-resolution 7T anatomical imaging [@keukenProbabilisticAtlasBasal2015], including the manual division of the striatum into the CN, Put, and VS reported in [@puckettUsingMultiechoSimultaneous2018]. As the goal of the analysis was to ascertain the sensitivity of each protocol to the contrasts of interest in each ROI, rather than seeking to assess any directional relationships between spatial attention and laterality of functional response, the left and right images of each ROI were joined to form a bilateral mask image. 
  
_Cortical ROIs_: The cortical regions of interest were identified using the Neurosynth meta-analytic association test from  [topic 303](https://neurosynth.org/analyses/topics/v4-topics-400/303), of the set [v4-topics-400](https://neurosynth.org/analyses/topics/v4-topics-400/), which contains the top-loading topic terms: attention, orienting, spatial, attentional, cued, target, cue, cueing and endogenous cues. This meta-analysis identified 5 ROIs including the left and right frontal eye fields (FEF), left and right intra-parietal sulcus (IPS), and the left lateral occipital complex (LOC). The approximate centre of each ROI was defined in MNI co-ordinates, and a sphere with a radius of 5 mm was defined around the co-ordinates using `fslmaths`. The resulting images were binarised and served as the cortical masks.

Each mask was transformed from MNI space to participant space using the ANTs `ApplyTransforms` wrapper, using the reverse of the transforms provided by fMRIprep [*from-MNI152NLin2009cAsym_to_t1w_mode-image_xfm.h5*]. Each mask file in subject space was then resliced (using SPM's `Reslice` wrapper) to match the dimensions of the functional images from each T2* protocol. 

**Functional data processing**
For each BOLD run, the following preprocessing was performed. First, a reference volume and its skull-stripped version were generated using a custom methodology of *fMRIPrep*. A deformation field to correct for susceptibility distortions was estimated based on *fMRIPrep*'s *fieldmap-less* approach. The deformation field is that resulting from co-registering the BOLD reference to the same-subject T1w-reference with its intensity inverted [@wangComparisonImageIntensity2017; @huntenburgLaminarPythonTools2017]. Registration is performed with `antsRegistration` (ANTs 2.2.0), and the process regularized by constraining deformation to be nonzero only along the phase-encoding direction, and modulated with an average fieldmap template [@treiberCharacterizationCorrectionGeometric2016]. Based on the estimated susceptibility distortion, a corrected EPI (echo-planar imaging) reference was calculated for a more accurate co-registration with the anatomical reference. The BOLD reference was then co-registered to the T1w reference using `bbregister` (FreeSurfer) which implements boundary-based registration [@greveAccurateRobustBrain2009]. Co-registration was configured with six degrees of freedom. Head-motion parameters with respect to the BOLD reference (transformation matrices, and six corresponding rotation and translation parameters) are estimated before any spatiotemporal filtering using `mcflirt` [FSL 5.0.9, @jenkinsonImprovedOptimizationRobust2002]. BOLD runs were slice-time corrected using `3dTshift` from AFNI 20160207 [@coxSoftwareToolsAnalysis1997, RRID:SCR_005927]. The BOLD time-series, were resampled to surfaces on the following spaces: *fsaverage*, *fsnative*. The BOLD time-series (including slice-timing correction) were resampled onto their original, native space by applying a single, composite transform to correct for head-motion and susceptibility distortions. These resampled BOLD time-series will be referred to as *preprocessed BOLD in original space*, or just *preprocessed BOLD*. The BOLD time-series were resampled into standard space, generating a *preprocessed BOLD run in 'MNI152NLin2009cAsym' space*. First, a reference volume and its skull-stripped version were generated using a custom methodology of *fMRIPrep*. Several confounding time-series were calculated based on the *preprocessed BOLD*: framewise displacement (FD), DVARS and three region-wise global signals. FD and DVARS are calculated for each functional run, both using their implementations in *Nipype* [following the definitions by @power_fd_dvars]. The three global signals are extracted within the CSF, the WM, and the whole-brain masks. 

Further pre-processing and analyses performed subsequent to running *fMRIprep* was completed using a computing environment defined by [a singularity container for which the recipe is available online](https://github.com/kel-github/code-4-seq-comp-test-7T/blob/master/Singularity). All remaining procedures were implemented using Nipype (version 1.6.0), ANTs 2.2.0, and SPM12-r7219, using a combination of [Python Jupyter notebooks and custom Matlab code that are available online](https://github.com/kel-github/code-4-seq-comp-test-7T). 
**Multi-echo combination**

Next, the multi-echo images were combined within each session, using a weighted summation as defined in Puckett et al, [-@puckettUsingMultiechoSimultaneous2018]. Specifically, weights were calculated per voxel, $w_n$, using the formula:

$w_n = \frac{AVG_n \cdot TE_n}{\sum AVG_n \cdot TE_n}$

where $AVG$ is the temporal average of the time-series. This weighting scheme carries the advantage that the weights can be directly estimated from the data, and no additional calibration scans or model assumptions are required. Moreover, this method has been shown to work as equally well as other combination schemes [@kettingerInvestigatingGroupLevelImpact2016]. 

### Single subject analysis
\label{sec:SingSub}

As we were concerned with the contrast-to-noise ratios observed within _a priori_ defined anatomical ROIs, we opted to conduct the analysis in subject space, rather than normalised space. This was motivated by the requirement for anatomical accuracy. Thus all the subsequent analyses were performed on the pre-processed BOLD (as defined above). We sought to examine protocol quality on two indices of interest; the tSNR ($\frac{\mu}{\sigma}$) and CNR for contrasts of theoretical interest.
  
#### tSNR 
\label{sec:tSNRMeth}

We computed tSNR for each functional run, by computing for each voxel the ratio between the mean and the standard deviation of the time series. The resulting tSNR images were then averaged over session for each subject, and the average tSNR was taken from each ROI, using `spm_read_vols` (to get the x, y, z coordinates for each ROI) and `spm_get_data` to extract the tSNR values from the voxels of interest. 

#### CNR
\label{sec:CNRMeth}

We sought to acertain the sensitivity of the three protocols to the experimental events of interest. We therefore computed for each voxel the $t$-score for activation strength relative to baseline, for a given condition mean. This is directly related to the computation for tSNR measures that quantify the amplitude of activation (relative to baseline), relative to the noise [@corbinAccurateModelingTemporal2018]. The resulting $t$-scores thus provide a measure of the sensitivity of each protocol to the key experimental events. To attain $t$-scores for the events of interest, T2* data were first temporally filtered using a highpass filter (cut-off 1/128 Hz) to remove slow drifts. Spatial smoothing was then applied, using a Gaussian kernel of 2 mm FWHM, as this was found to stabilise the $t$-score estimates. 

We next fit two GLMs to each participant's data; one that would allow computation of $t$-scores for conditions of overt action, and one for computation of $t$-scores for the attentional manipulations of interest. We opted to fit the two GLMs separately to the data as this allowed us to model the data with relatively simple GLMs, and response-hand was fully counterbalanced over the attentional manipulations. To model the effect of response hand, a GLM with two regressors were defined, one for left hand responses and one for right hand responses. To model the effect of the attentional manipulations, a second GLM was fit that contained 4 regressors, reflecting the 2 x 2 design of target laterality (left vs right) x spatial cue probability (p= .5 vs .8). GLMs were fit using the canonical double-gamma haemodynamic response function (HRF) [@fristonAnalysisFunctionalMRI1994, @fristonEventRelatedFMRICharacterizing1998, @fristonStatisticalParametricMaps1994, @gloverDeconvolutionImpulseResponse1999] with time and dispersion derivatives, and using the FAST option for pre-whitening [@corbinAccurateModelingTemporal2018]. GLM model specification and estimation were conducted using the `SpecifySPMModel`, `Level1Design` and `EstimateModel` wrapper functions from Nipype. 

We sought to determine the sensitivity of the three protocols to the following condition means of interest; left hand or right hand response, left or right target laterality, spatial cue certainty of p = .5 or p = .8, and left targets|p = .8 or right targets|p=.8. These latter two cells were chosen as they should reflect the strongest psychological response to the cue, and also a cell containing of the lowest number of trials that may be used to generate a mean value in a subsequent experiment. Therefore the last two contrasts show the weakest or worst case tSNR scenario for an experimental event of interest, where a psychological effect of interest is evident. Thus a total of eight $t$-contrasts (against zero) were applied. We now refer to the $t$-score measure as the contrast-noise-ratio (CNR). 

#### Assessment of recovered HRF functions
\label{sec:AssessHRF}

To assess visually whether the current protocols yielded a typical HRF in subcortical ROIs, a GLM was fit to each participant's data using a Finite Impulse Response (FIR) function (length: 18 seconds, order: 9). If a typical HRF function is present, then the parameters of the FIR should recover the HRF shape. To avoid potential overfitting to noise owing to the increase of number of parameters in the FIR function, a simplified design matrix was defined, which contained regressors for target laterality only. As above, this was achieved using the `SpecifySPMModel` and `Level1Design` Nipype wrappers. Prior to model estimation, and owing to the presence of overlapping trials within a condition (due to the fast event-related design of the protocols), the regressors were de-orthogonalised (within condition) using a custom adaptation of the [`spm_fMRI_design`](https://github.com/kel-github/code-4-seq-comp-test-7T/blob/master/spm_fMRI_design_copy.m) function. The resulting GLMs were estimated as above. 
  
#### Statistical Approach
\label{sec:StatsApproach}

Statistical analyses comparing the protocols were based on those presented in Puckett et al [-@puckettUsingMultiechoSimultaneous2018] and Miletic et al [-@mileticFMRIProtocolOptimization2020]. We extracted average tSNR or CNR scores per subject, protocol and ROI and applied linear mixed effects models with average tSNR or CNR scores as the dependent variable, using the lme4 package [@batesFittingLinearMixedEffects2015]. ROI, protocol, and contrast (where relevant) served as predictor variables, including all possible interaction terms. Random intercepts were included for each subject. Statistical significance of the predictor variables was assessed using Type II Wald chisquare tests, using the car package [foxCompanionAppliedRegression2019]. Statistically significant effects were followed up with post-hoc t-tests, with application of the Sidak adjustment for multiple comparisons [@sidakRectangularConfidenceRegions1967]. Where relevant, effect sizes were computed using Cohen's $d$. 

# Results
\label{sec:Results}

This and all subsequent analyses were conducted using R (version 3.3.2, [@Rcitation]) and RStudio (version 1.1.456, [@rstudiocitation]). 

## Behaviour
\label{sec:Behaviour}

Given the N of 5 participants, we present the influence of cue certainty on participant's behaviour for visual inspection (see Figure \@ref{fig:paradigm}, panel D), rather than applying inferential statistics, owing to the low statistical power for group-level inference. However, analysis of the individual participant data from the initial behavioural session demonstrated a statistically significant influence of both cue types (spatial and value) on each participant's response times (RTs). An online description of this data is available [here](). 

Outliers from correct response times (RTs) were defined as those less than 200 ms, or greater than 2.5 times the standard deviation above the mean for each participant, protocol and cueing condition, and were removed from the data. As both RT and accuracy are influenced by the certainty offered by spatial cues, an inverse efficiency score was computed for each participant, protocol and cueing condition by taking $\frac{RT_{mu}}{Acc}$. Given the widespread replication of the influence of spatial cues on visual selection [@chicaSpatialOrientingParadigm2014], including a very similar previously published paradigm [@garnerIncentiveValueSpatial2021], we interpret our data as reflecting a cost to visual selection at unlikely target locations (p=.2).

## Comparison of tSNR between protocols
\label{sec:tSNRResults}

First we sought to determine which protocol yielded the highest tSNR values across the _a priori_ defined ROIs. The tSNR data were extracted for each subject, protocol and ROI, the results of which are presented in Figure \@ref{fig:tSNR}. As can be seen from the example whole brain tSNR map, strongest tSNR was observed for the ME protocol, then for the 3D EPI, and last for the CMRR protocol. 

```{r loadtSNR, echo=FALSE, message=F, warning=F}

# Load and tidy data HAND GLM DATA

tSNR = read.csv('../data/tSNR_ROI_agg.csv')
tSNR $sub <- factor(tSNR$sub)
tSNR$TR <- factor(tSNR$TR)
tSNR$roi <- factor(tSNR$roi)
names(tSNR)[names(tSNR) == "contrast"] = "session"
tSNR$session <- factor(tSNR$session)
names(tSNR)[names(tSNR) == "tT"] = "tSNR"

tSNR$TR <- tSNR$TR %>% recode('700' = 'ME',
                              '1510' = 'CMRR',
                              '1920' = '3D')
tSNR <- tSNR %>% mutate(roi=factor(roi, levels = c('FEF', 'IPS', 'LOC', 'VS', 'CN', 'Put', 'GPe', 'GPi', 'STN')))

mutSNR <-tSNR %>% group_by(sub, TR, roi) %>%
                           summarise(tSNR = mean(tSNR)) %>%
                           ungroup()

```

```{r, tSNRanalysis, echo=FALSE, message=F, warning=F}

tsnr_mod <- lmer( tSNR ~ TR*roi+ (1|sub), data=mutSNR)
tst_tsnr_mod <- Anova(tsnr_mod, test.statistic="F")
# test cortical
cort_tsnr <- mutSNR %>% filter(roi == "FEF" | roi == "IPS" | roi == "LOC")
cort_tsnr_mod <- lmer(tSNR ~ TR*roi+ (1|sub), data = cort_tsnr)
tst_cort_tsnr_mod <- Anova(cort_tsnr_mod, test.statistic = "F")
# cortical follow up
cort_tsnr_me <- emmeans(cort_tsnr_mod, "TR")
cntrst_cort_tsnr_me <- contrast(cort_tsnr_me, 'tukey', adjust = 'sidak') 
cntrst_cort_tsnr_me <- cntrst_cort_tsnr_me %>% broom::tidy()
cntrst_cort_tsnr_me <- cntrst_cort_tsnr_me %>% filter(adj.p.value<.05)

# now testing subcortical
sc_tsnr <- mutSNR %>% filter(roi != "FEF" & roi != "IPS" & roi != "LOC")
sc_tsnr_mod <- lmer(tSNR ~ TR*roi+ (1|sub), data = sc_tsnr)
tst_sc_tsnr_mod <- Anova(sc_tsnr_mod, test.statistic = "F")
# subcortical follow up
sc_tsnr_int <- emmeans(sc_tsnr_mod, pairwise ~ TR|roi, adjust = 'sidak')
cntrst_sc_tsnr_int <- contrast(sc_tsnr_int, adjust = 'sidak') 
```

The tSNR scores differed by protocol, and this difference was modulated across ROIs. This was evidenced by a significant TR x ROI interaction (F(`r tst_tsnr_mod["TR:roi", "Df"]`, `r tst_tsnr_mod["TR:roi", "Df.res"]`) = `r tst_tsnr_mod["TR:roi", "F"]`, p = `r tst_tsnr_mod["TR:roi", "Pr(>F)"]`). To further investigate this interaction, and given the known signal differences between cortical and subcortical regions, the same analysis was applied separately to the cortical and the subcortical ROIs. Indeed, Figure \@ref{fig:tSNR}, panel B shows the signal advantage for a representative cortical ROI (IPS) relative to representative subcortical ROIs. For the cortical ROIs, tSNR differed between protocols consistently across the IPS, FEF and LOC. This was evidenced by a main effect of protocol (F(`r tst_cort_tsnr_mod["TR", "Df"]`, `r tst_cort_tsnr_mod["TR", "Df.res"]`) = `r tst_cort_tsnr_mod["TR", "F"]`, p = `r tst_cort_tsnr_mod["TR", "Pr(>F)"]`), whereas neither the main effect of ROI nor the protocol x ROI interaction achieved statistical significance (both ps > `r tst_cort_tsnr_mod["roi", "Pr(>F)"]`). With regard to the main effect of protocol, the ME protocol showed increased tSNR relative to the CMRR (t(`r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","df"]`) = `r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","statistic"]`, $d$ = `r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","estimate"]/(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","std.error"]*sqrt(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","df"]+1))`, p = `r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "ME - CMRR","adj.p.value"]`), and the 3D-EPI showed higher tSNR relative to the CMRR protocol (t(`r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","df"]`) = `r abs(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","statistic"])`, $d$ = `r abs(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","estimate"]/(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","std.error"]*sqrt(cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","df"]+1)))`, p = `r cntrst_cort_tsnr_me[cntrst_cort_tsnr_me$contrast == "CMRR - 3D","adj.p.value"]`). In contrast, the effect of protocol was modulated across subcortical ROIs, as was evidenced by a significant protocol x ROI interaction (F(`r tst_sc_tsnr_mod["TR:roi", "Df"]`, `r tst_sc_tsnr_mod["TR:roi", "Df.res"]`) = `r tst_sc_tsnr_mod["TR:roi", "F"]`, p = `r tst_sc_tsnr_mod["TR:roi", "Pr(>F)"]`). For each subcortical ROI, tSNR scores differed between each protocol with ME > 3D EPI > CMRR (all ps < .0001), apart from in the VS, where the difference between the ME and CMRR protocol did not reach statistical significance (p = .334). Overall, the ME protocol fared better in terms of tSNR across all ROIs, apart from in the VS, where it was not distinguishable from the 3D-EPI protocol.

```{r tSNR, out.width="50%", fig.cap="tSNR observed for the 3 protocols. A) tSNR across the whole brain for each protocol, for one example subject and session. B) Mean tSNR values from 3 key ROIs, across protocols (x-axis). Each line reflects data from one subject. ME = multi-echo, CMRR =, 3D = 3D Echo Planar Imaging, IPS = intra-parietal sulcus, CN = caudate nucleus, Put = putamen"}

tSNR_fig_pth <- '../images/tSNR_wholebrain_byReg.png' 
include_graphics(tSNR_fig_pth)
```


### Comparing CNR Between Protocols
\label{sec:CNRResults}

#### Thresholded voxels
\label{sec:Thrshvox}

Next we sought to determine which protocol yielded the highest CNR values, at the voxels that showed the strongest activations to the experimental manipulations of interest. To attain responsive voxels, each contrast image was thresholded at p<.001. First we examined the CNR values for each response hand (left or right > 0), by applying a linear mixed effects model to the response hand $t$-scores, with contrast (left or right hand) and protocol and their interaction as fixed factors, and a random effects intercept term for each subject.

```{r loadCNRdatT, echo=FALSE, message=F, warning=F}

# Load and tidy data HAND GLM DATA
tconts_thrsh = read.csv('../data/HANDS_activationC_tCNR_stat_vox_agg.csv')
tconts_thrsh$sub <- factor(tconts_thrsh$sub)
tconts_thrsh$TR <- factor(tconts_thrsh$TR)
tconts_thrsh$roi <- factor(tconts_thrsh$roi)
tconts_thrsh$contrast <- factor(tconts_thrsh$contrast)
names(tconts_thrsh)[names(tconts_thrsh) == "tT"] = "CNR"
tconts_thrsh$contrast <- tconts_thrsh$contrast %>%  recode('2' = 'left_hand',
                                                           '3' = 'right_hand') 

tmp = read.csv('../data/TC_activationC_tCNR_stat_vox_agg.csv')
tmp$sub <- factor(tmp$sub)
tmp$TR <- factor(tmp$TR)
tmp$roi <- factor(tmp$roi)
tmp$contrast <- factor(tmp$contrast)
names(tmp)[names(tmp) == "tT"] = "CNR"

tmp$contrast <- tmp$contrast %>% recode('4' = 'lft tgt',
                                        '5' = 'rght tgt',
                                        '6' = 'p8',
                                        '7' = 'p5',
                                        '8' = 'lft_p8',
                                        '9' = 'rght_p9')

tconts_thrsh <- rbind(tconts_thrsh, tmp)

tconts_thrsh$TR <- tconts_thrsh$TR %>% recode('700' = 'ME',
                                              '1510' = 'CMRR',
                                              '1920' = '3D EPI')
names(tconts_thrsh)[names(tconts_thrsh) == "contrast"] <- "comp"
mutConts <- tconts_thrsh %>% group_by(sub, TR, comp) %>%
                            summarise(mu = mean(CNR)) %>% ungroup()
rm(tmp)
```

```{r thrshlook, echo=FALSE, message=F, warning=F}
bpkpsubs <- with(mutConts %>% filter(comp == "left_hand" | comp == "right_hand"), boxplot(mu~comp*TR))
#bpkpsubs
```


```{r thrshLME_handT, echo=FALSE, message=F, warning=F}
thrshmod_handT <- lmer( mu ~ TR*comp + (1|sub), data = mutConts %>% filter(comp == "left_hand" | comp == "right_hand"))
thrshmod_handT_an <- Anova(thrshmod_handT, test.statistic="F")
```


```{r, thrsh_me_prot_FU, echo=TRUE, results="hide"}
thrsh_handT_me_prot <- emmeans(thrshmod_handT, "TR")
thrsh_handT_me_cont <- contrast(thrsh_handT_me_prot, 'tukey', adjust = 'sidak') 
thrsh_handT_me_cont <- thrsh_handT_me_cont %>% broom::tidy()
thrsh_handT_me_prot <-thrsh_handT_me_prot %>% broom::tidy()
thrsh_handT_me_cont
```  

The data from this analysis are presented in see Figure \@ref{fig:thrshCNR}, panels A & B. CNR differed between protocols, as evidenced by a significant main effect (F(`r thrshmod_handT_an["TR", "Df"]`, `r thrshmod_handT_an["TR", "Df.res"]`) = `r thrshmod_handT_an["TR", "F"]`, `r thrshmod_handT_an["TR", "Pr(>F)"]`. Post-hoc contrasts showed that CNR values were statistically higher for the ME protocol (mean = `r thrsh_handT_me_prot %>% filter(TR == "ME") %>% select("estimate")`, sd = `r thrsh_handT_me_prot %>% filter(TR == "ME") %>% select("std.error")*sqrt(thrsh_handT_me_prot %>% filter(TR == "ME") %>% select("df"))`) relative to the CMRR protocol (mean = `r thrsh_handT_me_prot %>% filter(TR == "CMRR") %>% select("estimate")`, sd = `r thrsh_handT_me_prot %>% filter(TR == "CMRR") %>% select("std.error")*sqrt(thrsh_handT_me_prot %>% filter(TR == "CMRR") %>% select("df"))`, t(`r thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(df)`) = `r thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(statistic)`, $d$ = `r thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(estimate) / (thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(std.error)*sqrt(thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(df)))`, p = `r thrsh_handT_me_cont %>% filter(contrast == "ME - CMRR") %>% select(adj.p.value)`), and relative to the 3D EPI protocol (mean = `r thrsh_handT_me_prot %>% filter(TR == "3D EPI") %>% select("estimate")`, sd = `r thrsh_handT_me_prot %>% filter(TR == "3D EPI") %>% select("std.error")*sqrt(thrsh_handT_me_prot %>% filter(TR == "3D EPI") %>% select("df"))`, t(`r thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(df)`) = `r thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(statistic)`, $d$ = `r thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(estimate) / (thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(std.error)*sqrt(thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(df)))`, p = `r thrsh_handT_me_cont %>% filter(contrast == "ME - 3D EPI") %>% select(adj.p.value)`). Moreover, and in contrast to the tSNR values, CNR for the CMRR protocol was statistically higher than for the 3D EPI protocol ( t(`r thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(df)`) = `r thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(statistic)`, $d$ = `r thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(estimate) / (thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(std.error)*sqrt(thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(df)))`, p = `r thrsh_handT_me_cont %>% filter(contrast == "CMRR - 3D EPI") %>% select(adj.p.value)`). Neither the main effect of contrast nor the protocol x contrast interaction achieved statistical significance (both ps > `r min(thrshmod_handT_an[thrshmod_handT_an[,"Pr(>F)"] > .05, "Pr(>F)"])`). 


```{r thrshCNR, out.width="70%", fig.cap="CNR from voxels thresholded at p< .001 for each contrast. A) CNR values from the left response hand activation contrast for one representative subject and session. B) Densities of CNR scores for both the left and right hand response for each protocol. C) Showing the left target laterality contrast for the same subject and session as panel A. D) Beta estimates (y-axis) across time (x-axis) as estimated by a FIR model. The model recovered a typical HRF function. ME = multi-echo, CMRR =, 3D = 3D Echo Planar Imaging, CNR = contrast noise ratio, t = time."}

thrsh_CNR_fig_pth <- '../images/ActStatsT_hands_CNR.pdf' 
include_graphics(thrsh_CNR_fig_pth)
```

```{r thrshLME_handT, echo=FALSE, message=F, warning=F}
thrshmod_TCT <- lmer( mu ~ TR*comp + (1|sub), data = mutConts %>% filter(comp == "lft tgt" | comp == "rght tgt"))
thrshmod_TCT_an <- Anova(thrshmod_TCT, test.statistic="F")
```

```{r thrshLME_handT, echo=FALSE, message=F, warning=F}
thrshmod_pspatial_T <- lmer( mu ~ TR*comp + (1|sub), data = mutConts %>% filter(comp == "p8" | comp == "p5"))
thrshmod_pspatial_an <- Anova(thrshmod_pspatial_T, test.statistic="F")
```

```{r thrshLME_handT, echo=FALSE, message=F, warning=F}
thrshmod_lat_pspatial_T <- lmer( mu ~ TR*comp + (1|sub), data = mutConts %>% filter(comp == "lft_p8" | comp == "rght_p9"))
thrshmod_lat_pspatial_an <- Anova(thrshmod_lat_pspatial_T, test.statistic="F")
```

```{r, concatCNRps, echo=FALSE, message=F, warning=F}
thrsh_CNR_ps <- c(thrshmod_TCT_an[,"Pr(>F)"], thrshmod_pspatial_an[,"Pr(>F)"], thrshmod_lat_pspatial_an[,"Pr(>F)"]) 
thrsh_CNR_ps <- thrsh_CNR_ps[thrsh_CNR_ps > .05]
```

The main effect and pattern of protocol differences was consistent across the remaining analyses, whether CNR data were computed using the target laterality (left or right) contrasts (F(`r thrshmod_TCT_an["TR", "Df"]`, `r thrshmod_TCT_an["TR", "Df.res"]`) = `r thrshmod_TCT_an["TR", "F"]`, p = `r thrshmod_TCT_an["TR", "Pr(>F)"]`), the spatial cue probability contrasts (p=.8 or p=.5, F(`r thrshmod_pspatial_an["TR", "Df"]`, `r thrshmod_pspatial_an["TR", "Df.res"]`) = `r thrshmod_pspatial_an["TR", "F"]`, p = `r thrshmod_pspatial_an["TR", "Pr(>F)"]`) or the target laterality|p = .8 contrasts (F(`r thrshmod_lat_pspatial_an["TR", "Df"]`, `r thrshmod_lat_pspatial_an["TR", "Df.res"]`) = `r thrshmod_lat_pspatial_an["TR", "F"]`, p = `r thrshmod_lat_pspatial_an["TR", "Pr(>F)"]`). Also consistent was the absence of statistically significant influences of contrast, or any contrast x protocol interactions (all ps > `r min(thrsh_CNR_ps)`). Therefore, across all modelled experimental events of interest, the ME protocol outperformed the CMRR protocol which in turn outperformed the 3D EPI. 

#### Regions of interest
\label{sec:CNR_ROI}

```{r load_roi_act, echo=FALSE, message=F, warning=F}

# Load and tidy data HAND GLM DATA
roi_act= read.csv('../data/HANDS_tCont_quantCNR_ROI_agg.csv')
roi_act$sub <- factor(roi_act$sub)
roi_act$TR <- factor(roi_act$TR)
roi_act$roi <- factor(roi_act$roi)
roi_act$contrast <- factor(roi_act$contrast)
names(roi_act)[names(roi_act) == "tT"] = "CNR"
roi_act$contrast <- roi_act$contrast %>%  recode('LH' = 'lft_hnd',
                                                 'RH' = 'rght_hnd') 

tmp = read.csv('../data/TC_tCont_quantCNR_ROI_agg.csv')
tmp$sub <- factor(tmp$sub)
tmp$TR <- factor(tmp$TR)
tmp$roi <- factor(tmp$roi)
tmp$contrast <- factor(tmp$contrast)
names(tmp)[names(tmp) == "tT"] = "CNR"

##### checking extraction code
roi_act <- rbind(roi_act, tmp)

roi_act$TR <- roi_act$TR %>% recode('700' = 'ME',
                                    '1510' = 'CMRR',
                                    '1920' = '3D EPI')

rm(tmp)
```

```{r tst_roi_act_hnds, echo=FALSE, message=F, warning=F}

roi_act_hands <- lmer( CNR ~ TR*contrast*q*roi + (1|sub), data = roi_act %>% filter(contrast == "lft_hnd" | contrast == "rght_hnd"))
roi_act_hands_an <- Anova(roi_act_hands, test.statistic="F")
roi_act_hands_an
```
```{r, FU}
# follow up the interaction at each roi
rois <- unique(roi_act$roi)

post_hoc <- lapply(unique(roi_act$roi), function(x) Anova(lmer( CNR ~ TR*contrast*q + (1|sub), data = roi_act %>% filter(contrast == "lft_hnd" | contrast == "rght_hnd") %>% filter(roi == x)), test.statistic="F"))
names(post_hoc) <- unique(roi_act$roi)
```



```{r, follow_up_roi_hand_act, echo=FALSE, message=F, warning=F}

roi_act_hands_mus <- emmeans(roi_act_hands, ~TR|q|roi)
roi_act_hands_cont <- contrast(roi_act_hands_mus, 'tukey', adjust = 'sidak')

thrsh_handT_me_cont <- contrast(thrsh_handT_me_prot, 'tukey', adjust = 'sidak') 
thrsh_handT_me_cont <- thrsh_handT_me_cont %>% broom::tidy()
thrsh_handT_me_prot <-thrsh_handT_me_prot %>% broom::tidy()
thrsh_handT_me_cont

roi_tsnr_mus <- emmeans(roi_SNR_mod, ~TR | roi)
roi_tsnr_cont <- contrast(roi_tsnr_mus, 'tukey', adjust = 'sidak')
roi_tsnr_cont <- roi_tsnr_cont  %>% broom::tidy()
roi_tsnr_cont


```










```{r loadCNRdat, echo=FALSE, message=F, warning=F}

# Load and tidy data HAND GLM DATA
CNR = read.csv('../data/HANDSs_tCNR_stat_vox_agg.csv')
CNR$sub <- factor(CNR$sub)
CNR$TR <- factor(CNR$TR)
CNR$roi <- factor(CNR$roi)
CNR$contrast <- factor(CNR$contrast)
names(CNR)[names(CNR) == "tT"] = "CNR"
CNR$contrast <- CNR$contrast %>%  recode('1' = 'left_vs_right_hand') 

tmp = read.csv('../data/TC_tCNR_stat_vox_agg.csv')
tmp$sub <- factor(tmp$sub)
tmp$TR <- factor(tmp$TR)
tmp$roi <- factor(tmp$roi)
tmp$contrast <- factor(tmp$contrast)
names(tmp)[names(tmp) == "tT"] = "CNR"

tmp$contrast <- tmp$contrast %>% recode('1' = 'tgt side',
                                        '2' = 'cert',
                                        '3' = 'cert x tgt side')

CNR <- rbind(CNR, tmp)

CNR$TR <- CNR$TR %>% recode('700' = 'ME',
                            '1510' = 'CMRR',
                            '1920' = '3D EPI')
names(CNR)[names(CNR) == "contrast"] <- "comp"
muCNR <- CNR %>% group_by(sub, TR, comp) %>%
                 summarise(mu = mean(CNR))

```


```{r thrshlook, echo=FALSE, message=F, warning=F}
bpthrsh <- with(muCNR, boxplot(mu~contrast*TR))
```

```{r thrshLME, echo=FALSE, message=F, warning=F}
thrshmod <- lmer( mu ~ TR*contrast + (1|sub), data=muCNR)
thrsh_lme_an <- Anova(thrshmod, test.statistic="F")
thrsh_lme_an
```

```{r, thrsh_me_prot_FU, echo=TRUE, results="hide"}
thrsh_me_prot <- emmeans(thrsh_mod, "TR")
thrsh_me_cont <- contrast(thrsh_me_prot, 'tukey', adjust = 'sidak') 
thrsh_me_cont <- thrsh_me_cont %>% broom::tidy()
```  

```{r, thrsh_me_cntrst_FU, echo=TRUE, results="hide"}
thrsh_me_cont_mu <- emmeans(thrsh_mod, "comp")
thrsh_me_cont_cont <- contrast(thrsh_me_cont_mu, 'tukey', adjust = 'sidak') 
thrsh_me_cont_cont <- thrsh_me_cont_cont %>% broom::tidy()
thrsh_me_cont_cont <- thrsh_me_cont_cont %>% filter(adj.p.value<.05)
```  

```{r thrshCNR, out.width="70%", fig.cap="CNR from voxels thresholded at p< .001 for each contrast. A) CNR values from the response hand contrast for one representative subject and session. B) Densities of CNR scores. Overall, the ME protocol showed higher mean CNR scores than the 3D EPI sequence. C) Showing the target laterality x cue probability contrast for the same subject and session as panel A. D) Beta estimates (y-axis) across time (x-axis) as estimated by a FIR model. The model recovered a typical HRF function. ME = multi-echo, CMRR =, 3D = 3D Echo Planar Imaging, CNR = contrast noise ratio, t = time."}

thrsh_CNR_fig_pth <- '../images/thrsh_CNR.png' 
include_graphics(thrsh_CNR_fig_pth)
```

Next we sought to determine which protocol yielded the highest CNR values, taking into account the voxels that showed the strongest response to the experimental manipulations of interest (response hand, target laterality, cue probability, and the cue probability x target laterality interaction). In accordance with the findings from the tSNR measure above, the ME protocol yielded statistically higher CNR relative to the 3D EPI sequence (t(`r thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "df"]`) = `r thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "statistic"]`, $d$ = `r thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "estimate"] / (thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "std.error"]*sqrt(thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "df"]+1))`, p = `r thrsh_me_cont[thrsh_me_cont$contrast == "ME - 3D EPI", "adj.p.value"]`). However, unlike the findings pertaining to tSNR, none of the other comparisons achieved statistical siginifance (`r min(thrsh_me_cont$adj.p.value[thrsh_me_cont$adj.p.value > .05])`). As anticipated, the response hand contrast yielded higher CNR values than the remaining contrasts (all ps < .0001, $d$ range = [`r thrsh_me_cont_cont[1,"estimate"] / (thrsh_me_cont_cont[1,"std.error"]*sqrt(thrsh_me_cont_cont[1,"df"]+1))`, `r thrsh_me_cont_cont[3,"estimate"] / (thrsh_me_cont_cont[3,"std.error"]*sqrt(thrsh_me_cont_cont[3,"df"]+1))`]. Overall, the ME fared better than the 3D EPI sequence, however the advantage relative to the CMRR protocol found with the tSNR scores was not found in this CNR data.

#### ROI CNR

Next we sought to determine whether the advantage of the ME sequence remained evident when the CNR data was taken from the _a priori_ defined ROIs. We extracted CNR values for each ROI and computed an average CNR score for each. Visual inspection of the data showed that one of the participants scored greater than 3 standard deviations from the group mean on all measures. Therefore their data is excluded from the subsequent analysis. 

```{r loadROICNRdat, echo=FALSE, message=F, warning=F}

# Load and tidy data
roi_cnr = read.csv('../data/TC_tCNR_ROI_agg.csv')
roi_cnr$sub <- factor(roi_cnr$sub)
roi_cnr$TR <- factor(roi_cnr$TR)
roi_cnr$roi <- factor(roi_cnr$roi)
roi_cnr$contrast <- factor(roi_cnr$contrast)
names(roi_cnr)[names(roi_cnr) == "tT"] = "CNR"
roi_cnr$contrast <- roi_cnr$contrast %>% recode('1' = 'tgt side',
                                        '2' = 'cert',
                                        '3' = 'cert x tgt side')
roi_cnr$TR <- roi_cnr$TR %>% recode('700' = 'ME',
                                    '1510' = 'CMRR',
                                    '1920' = '3D')
roi_cnr <- roi_cnr %>% mutate(roi=factor(roi, levels = c('FEF', 'IPS', 'LOC', 'VS', 'CN', 'Put', 'GPe', 'GPi', 'STN')))

tmp <- read.csv('~/Dropbox/documents/MC-Docs/seqtest-writeup/data/HANDS_tCNR_ROI_agg.csv')
names(tmp)[names(tmp) == "tT"] = "CNR"
tmp$contrast <- "resp hand"
tmp$TR <- factor(tmp$TR)
tmp$TR <- tmp$TR %>% recode('700' = 'ME',
                            '1510' = 'CMRR',
                            '1920' = '3D')
roi_cnr <- rbind(roi_cnr, tmp)

```


```{r, boxplot, echo=TRUE, results="hide"}

with(roi_cnr, boxplot(CNR~contrast*roi*TR))
with(roi_cnr %>% filter(sub != "1"), boxplot(CNR~contrast*roi*TR)) # sub 1 = outlier, remove
roi_cnr <-roi_cnr %>% filter(sub != "1")
```

```{r, stats_bl_conts, echo=TRUE, results="hide"}

# this code shows the main effect of TR, and then shows the followup comparisions
roi_SNR_mod <- lmer( CNR ~ TR*roi*contrast + (1|sub), data=roi_cnr )
roi_SNR_mod_an <- Anova(roi_SNR_mod, test.statistic="F")

```

```{r, tSNR_TR_roi_int, echo=TRUE, results="hide"}
roi_tsnr_mus <- emmeans(roi_SNR_mod, ~TR | roi)
roi_tsnr_cont <- contrast(roi_tsnr_mus, 'tukey', adjust = 'sidak')
roi_tsnr_cont <- roi_tsnr_cont  %>% broom::tidy()
roi_tsnr_cont
```

Comparable to the tSNR data, the extent to which CNR values differed between protocols was modulated by the ROI factor, as evidenced by a protocol x ROI interaction (F(`r roi_SNR_mod_an["TR:roi","Df"]`, `r roi_SNR_mod_an["TR:roi","Df.res"]`) = `r roi_SNR_mod_an["TR:roi","F"]`, p = `r roi_SNR_mod_an["TR:roi","Pr(>F)"]`). However, the pattern of modulation was different for the CNR data, relative to the tSNR data. Of the cortical ROIs, only the IPS region showed a pattern of CNR values that matched the tSNR findings, where the ME protocol yielded higher CNR values relative the CMRR protocol (t(`r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "df"]`) = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "statistic"]`, $d$ = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "estimate"]/(roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "std.error"] * sqrt(roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "df"]+1))`, p = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - CMRR", "adj.p.value"]`), and to the 3D-EPI protocol (t(`r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "df"]`) = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "statistic"]`, $d$ = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "estimate"]/(roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "std.error"] * sqrt(roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "df"]+1))`, p = `r roi_tsnr_cont[roi_tsnr_cont$roi == "IPS" & roi_tsnr_cont$contrast == "ME - 3D", "adj.p.value"]`), albeit to a small effect (see Figure \@ref(fig:cortCNR), panels A and B). CNR values from the LOC ROI were also statistical higher for the ME relative to the 3D EPI sequence (t(`r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "df"]`) = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "statistic"]`, $d$ = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "estimate"]/(roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "std.error"] * sqrt(roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "df"]+1))`, p = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "ME - 3D", "adj.p.value"]`). In contrast to the tSNR and IPS CNR findings, CNR was also higher for the CMRR relative to the 3D EPI sequence (t(`r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "df"]`) = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "statistic"]`, $d$ = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "estimate"]/(roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "std.error"] * sqrt(roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "df"]+1))`, p = `r roi_tsnr_cont[roi_tsnr_cont$roi == "LOC" & roi_tsnr_cont$contrast == "CMRR - 3D", "adj.p.value"]`) . However, visual inspection of the CNR images (see Figure \@ref(fig:cortCNR), panel C) suggests that this difference may be driven by a single subject, and therefore may reflect a spurious difference. All remaining comparisions did not achieve statistical significance.

```{r, cortCNR, out.width="80%", fig.cap="CNR data from cortical regions of interest. A) CNR values for the target laterality x cue probability contrast from each protocol (columns) for two representative subjects (rows) with the IPS region outlined in blue. B) Average CNR scores by subject for each protocol (x-axis) and cortical region (panels). The ME protocol showed higher mean CNR scores than the CMRR protocol. C) Same as panel A, but with the LOC region outlined in blue. P = protocol, ME = multi-echo, CMRR =, 3D EPI = 3D Echo Planar Imaging, CNR = contrast noise ratio, IPS = intraparietal sulcus, FEF = frontal eye fields, LOC = lateral occipital complex, sub = subjects."}

cort_CNR_fig_pth <- '../images/CNR_cortical_story.png' 
include_graphics(cort_CNR_fig_pth)

```


In contrast, no statistical differences between were detected when CNR values from the subcortical ROIs were compared between protocols (all ps > `r min(roi_tsnr_cont$adj.p.value[roi_tsnr_cont$adj.p.value > .05])`). The CNR images are presented in Figure \@ref{fig:subcortCNR}. Minimal CNR values were observed across subcortical ROIs (see Figure \@ref{fig:subcortCNR} panels A & B for CNR data from the response hand and target laterality x cue probability contrasts respectively, and panel C for the mean CNR values for two example subcortical ROIs). Visual inspection of the parameters recovered by the FIR model showed a typical HRF shape for the subcortical ROIs (panel D), which was much lower in amplitude relative to the parameters recovered from the cortical ROIs. 


```{r, subcortCNR, out.width="70%", fig.cap="CNR data from subcortical regions of interest. A) CNR values from a representative subject for the response hand contrast from each protocol (columns) for the CN and Put (rows, outlined). B) CNR values from the target laterality x cue probability contrast with the same configuration as panel A. C) Mean CNR values for each protocol (x-axis) for the CN and Put (panels). Each line reflects one subject. D) Parameters recovered by the FIR function for the IPS, CN and Put."}

subcort_CNR_fig_pth <- '../images/CNR_subcortical_story.png' 
include_graphics(subcort_CNR_fig_pth)

```


  





